\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{{./images}}
\title{ONLINE ART GALLERY \\ Update 10}
\date{1 April 2022}
\author{Abhinav Kumar \\ Roll No: 19111001 }
\begin{document}
\maketitle
\begin{center}
    \section*{\textbf{MODULES}} 
\end{center}
The project include following main modules:
\\
\begin{itemize}
    \item \textbf{Login of the User and Applicant.}
\item \textbf{ Registration of user.}
\item \textbf{Art description.}
\item \textbf{ User profile information.}
\item \textbf{The validation master.}
\item \textbf{Report genaration}
\item \textbf{Brief description of the all modules.}
\end{itemize}
\section*{Login of the Art Gellery -applicant and administrator : }
This module is considered with login of new user and administrator. Every user must enter his some details about itself for login the home page and after submitted he can Cart and ship Art online. The administrator can also login from this module. He can insert, delete or update the user login name and password.this module check the authenticity of the person accessing the project. The main objective behind this module is to provide security to the project so that access is restricted to the authorized users.
            Input is taken as login and password that the user Enters.
            This login id and password sent back to the activeX exe through DLL to check the information in the database.
            If the login id and password entered by the user matches those of the database file then it will return and redirected to respective control panel, other wise give a Error massage “login denied”.
\section*{Registration of the user : }
It takes the information the user and enter it into the database. This module uses the table ‘Documentations for its operation.
This table has following sub module
\begin{itemize}
    \item Add
\item Edit
\item Save
\item Delete
\end{itemize}
\\
\section*{Art Description : }
It takes the information form the Art and enters it into database. This module user the table ‘Art’ for its operation.
This table has following sub module.
\begin{itemize}
    \item Add
\item Edit
\item Update
\item Delete
\end{itemize}
\\
\section*{Art Info : }
It takes the information form the user and enters it into database. This module user the table. ‘ Art ’ for its operation
\section*{Artist Profile Info : }
It table the information the user enters it into database. This module user the table ‘Arist for its operation.This table user has following sub module:-
\begin{itemize}
    \item Add
\item Update
\item Delete
\end{itemize}
\section*{Validation Master : }
This module validation the entry made by user if the entry is not as per the specification a wrong message is given.
\end{document}