\documentclass{article}
\usepackage[utf8]{inputenc}
\title{ONLINE ART GALLERY \\ Update1}
\date{20 jan 2022}
\author{Abhinav Kumar }
\begin{document}
\maketitle
\begin{center}
   \section*{\textbf{OBJECTIVE}} 
\end{center}
The objectives of developing the Art Gellery are as given below: -
\\
\\
\begin{itemize}
    \item To store data of the entire user who are registered in the site.
    \item To solve the user’s problem in time efficient manner. Helping the user to search different Art with a robust search tools.
    \item Online updating of all type of Art, updating data using web based interfaces and with the help of buttons and links in an easy and convenient way.
    \item Data security is maintained to relatively high level by implementing it at Database level, so as to ensure that only authorized users have access to confidential User information.
    \item Developing a viable candidate system that fulfill the Faster and accurate information retrieval.
\end{itemize}
\begin{center}
   \section*{\textbf{ABSTRACT}} 
\end{center}
The main purpose of this term paper, entitled as “Online Art Gallery Management System” is to provide the facility of displays and sell art works of artist irrespective of their nationality, gender and other narrow consideration, through auction. Artist can register online for being a member in the art gallery and each artist can upload the digital copy of their art work under the respective categories. They can host their art work either for auction or for fixed price. The artist is liable to pay a fraction of the price of each art work to the web site to find the running fund for site.Art lovers have to go to the art exhibition to collect their favorite arts or painting.
\\
\\
\begin{center}
   \section*{\textbf{INTRODUCTION}} 
\end{center}
Online Art Gallery is an online application, which is used to display and sell art works of artist irrespective of their nationality, gender and other narrow consideration, through auction. Artist can register online for being a member in the art gallery and each artist can upload the digital copy of their art work under the respective categories. They can host their art work either for auction or for fixed price. The artist is liable to pay a fraction of the price of each art work to the web site to find the running fund for site.Art lovers have to go to the art exhibition to collect their favorite arts or painting. But now-a-days they are not getting enough time to go to the galleries and collect the arts and paintings.
\\
\\
\\
\\
\textbf{*************************END OF 1ST UPDATE***********************}
\end{document}
