\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{{./images}}
\title{ONLINE ART GALLERY \\ Update 11}
\date{8 April 2022}
\author{Abhinav Kumar \\ Roll No: 19111001 }
\begin{document}
\maketitle
\begin{center}
   \section*{\textbf{REPORT GENERATION}}
\end{center}
\begin{itemize}
    \item How many user are currently wring the site.
\item How many Artist are are currently wring the site.
\item How many Art are are currently wring the site.
\item Report on Purchased Arts.
\item For Art seeker on the basis of Art search by option.
\item Search by User Name.
\item Search by data.
\item Report of Shipped Records.
\item Report on the basis of user particulars.
\item Report of the registered user who have user id and password.
\end{itemize}
\\
\section*{Registered Module : }In this module, User enters a login & password and the software checks its validity. If the login & password is valid then he is allowed to enter, otherwise “Invalid User/Password” message is displayed. Different data access rights are assigned to different users.
\section*{ Master Module : } This module is used to add and manage user, Art and Artist details etc.
\section*{ Shipping Module: }In this module, User purchased art and get this art his location by shipping with two option, Online Cash Payment and Cash on delivery.
\section*{Modifying/Updating Existing Entries : }In this module, whenever an existing entity is required to be modified the corresponding forms are opened and the database is manipulated and the data is fetched. Now the user can made the required changes and then accordingly, he updates the data. Again, the checks are followed in case there is any invalid entry.
\section*{Searching : }In this module, User can search on the requirement their choice that mean, it (search engine) will help to search in all record/ information of available Art/Artist.
\section*{ Validation of Data Entered by the User & Error Handling : }In this module, the validity of data entered by the user during the various business processes is checked through various validation checks. For example, there should not be any characters entered in the numeric fields, likewise if there is any error occurs than it should handle that particular error and give the required messages.

\end{document}